Wigglyhedra

### 2024-06-14 draft/wigglyhedra.tex
one more remark and some bibentries missing

\para{Polyhedral geometry}
We then switch to geometric realizations of the wiggly complex~$\wigglyComplex_n$.
Our constructions are inspired by similar constructions for generalized associahedra~\cite{HohlwegLangeThomas,HohlwegPilaudStella} for finite type cluster algebras~\cite{FominZelevinski-clusterAlgebrasI,FominZelevinski-clusterAlgebrasII}, and for gentle associahedra for support $\tau$-tilting complexes on gentle algebras~\cite{PaluPilaudPlamondon}.
Namely, we first construct a fan supported by certain $\b{g}$-vectors of the wiggly arcs.

@@

\begin{remark}
\vincent{todo}
\end{remark}

@@

>>>>

\para{Polyhedral geometry}
We then switch to geometric realizations of the wiggly complex~$\wigglyComplex_n$.
Our constructions are inspired by similar constructions for generalized associahedra~\cite{HohlwegLangeThomas,HohlwegPilaudStella} for finite type cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasI,FominZelevinsky-ClusterAlgebrasII}, and for gentle associahedra for support $\tau$-tilting complexes on gentle algebras~\cite{PaluPilaudPlamondon-nonkissing}.
Namely, we first construct a fan supported by certain $\b{g}$-vectors of the wiggly arcs.

@@

@@

\begin{remark}
We want to stress out the important difference between our wiggly dissections and the noncrossing arc diagrams of~\cite{Reading-arcDiagrams}.
Our wiggly arcs and our crossing condition coincide with that of~\cite{Reading-arcDiagrams}.
However, for two arcs~$\alpha$ and~$\alpha'$ to be compatible, we forbid the left endpoint of~$\alpha$ to coincide with the right endpoint of~$\alpha'$, but allow $\alpha$ and~$\alpha'$ to have the same left endpoints or the same right endpoints, while N.~Reading does the opposite in~\cite{Reading-arcDiagrams}.
This results in very different objects.
\end{remark}
